`flippant` -- An `R` package for the automated  analysis of dithionite

### 2015-09-17 inst/manuscript/manuscript.rmd
Continuous editing ...;

#Installation
`flippant` has been integrated into the `bioconductor` collection of tools for 
biomedical data analysis [@huber_orchestrating_2015] and is thus installable and
loadable as follows from within a functioning `R` environment:
```{r eval = FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite(pkgs = "flippant")
library(flippant)
```
The package depends on the following, automatically satisfied extensions to `R`
base functionality: `r flippant_dependencies`

>>>>

#Installation
`flippant` has been integrated into the `bioconductor` collection of tools for 
biomedical data analysis [@huber_orchestrating_2015] and is thus install- and
loadable as follows from within a functional `R` environment:
```{r, eval = FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite(pkgs = "flippant")
library(flippant)
```
The package depends on the following packaged extensions to `R` base 
functionality, which are automatically satisfied on installation: 
`r flippant_dependencies`.
